Response to reviewers

### 2025-07-04 src/docs_paper-jtb/revisions.Rmd
Draft ELGM response

Response here.

>>>>

We have added the following text in Section 2.2 with the aim of making the mapping between the latent field and structured additive predictor of the Naomi model clearer:

> Equations...

We are not aware of any named smaller class of ELGMs to which the Naomi model belongs.
The available convergence theory for ELGMs is very restrictive and it is not clear whether or how the available results apply to the Naomi model; accordingly, we do not make any claims about theoretical performance in the present paper.
Our empirical analysis shows that we obtain results that are practically similar to gold-standard NUTS results.
